\\Large The heat is on: Rising temperatures alter when, how, and where large terrestrial mammals move

### 2025-06-12 writing/manuscript.Rmd
renamed "displ" to "distance"

```{r s-dist, fig.cap="\\textbf{Climate change will impact each species' movement rates differently.} The color scale indicates the predicted changes in distance traveled in 2100, relative to each location's average distance in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.72 to 1.29). The predictions only account for the predicted temperature throughout the province and ignore environmental factors such as terrain slope, soil type, and forest cover."}
knitr::include_graphics('../figures/bc-displ-2100.png')
```

>>>>

```{r s-dist, fig.cap="\\textbf{Climate change will impact each species' movement rates differently.} The color scale indicates the predicted changes in distance traveled in 2100, relative to each location's average distance in 2025 across all four scenarios, such that 1 indicates no change, values < 1 indicate a decrease, and values > 1 indicate an increase. For ease of readability, the color bar is on the $\\log_2$ scale to help visualize patterns in doubling, and values are capped to 0.67 and 1.5 ($\\approx 2^{\\pm 0.585}$; original data ranged 0.72 to 1.29). The predictions only account for the predicted temperature throughout the province and ignore environmental factors such as terrain slope, soil type, and forest cover."}
knitr::include_graphics('../figures/bc-distance-2100.png')
```
